### 2011-12-06 presentations/extended_source_search/lande_ext_collab_august_2011/introduction.tex
moving

\begin{frame}{Overview}
  \begin{itemize}
    \item Category II Paper
    \item Contact Authors: J. Lande, M. Ackermann, S. Funk
    \item Full author list being finalized
    \item Internal Referees: Marianne Lemoine-Goumard and Johann Cohen-Tanugi
    \item Target Journal: ApJ
    \item Status (something about being submitted to internal referees XXXX)
  \end{itemize}
\end{frame}

\begin{frame}{Paper Outline}
  \begin{itemize}
    \item Description of a new method (\pointlike) for analyzing extended sources.
    \item Monte Carlo calculation of false detection rate for extended sources.
    \item Calculation of the LAT's sensitivity to spatially extended sources
    \item Presentation of a new search for spatially extended sources:
      \begin{itemize}
        \item reanalyzing the extension of the 12 extended sources in 2FGL
        \item testing AGN from 2LAC for extension to validate the analysis
        \item presenting on the discovery/interpretation of several new extended sources not in 2FGL.
      \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Overview}
  \begin{itemize}
    \item Category II Paper
    \item Contact Authors: J. Lande, M. Ackermann, S. Funk
    \item Internal Referees: Marianne Lemoine-Goumard and Johann Cohen-Tanugi
    \item Target Journal: ApJ
    \item Currently submitted to internal referees
    \item Feedback welcome
  \end{itemize}
\end{frame}

\begin{frame}{Paper Outline}
  \begin{itemize}
    \item Description of a new method (\texttt{pointlike}) for analyzing extended sources.
    \item Monte Carlo calculation of false detection rate for extended sources.
    \item Calculation of the LAT's detection threshold 
      to spatially extended sources
    \item Presentation of a new search for spatially extended sources:
      \begin{itemize}
        \item Reanalyzing extension of 12 extended sources in 2FGL
        \item Test AGN from 2LAC for extension to validate the analysis
        \item Present 9 extended sources not in 2FGL
      \end{itemize}
  \end{itemize}
\end{frame}
